README

### 2022-09-29 rmd/supporting_info.Rmd
misc
Update supporting_info.Rmd
rmd

**Species interaction.** We analyzed a subset of our data to estimate the strength of interspecific interactions among stream fishes. In this analysis, we focused on `r n_distinct(df_complete$site_id)` sites with $>16$ years of observations and no intentional release of masu salmon. These additional constraints were necessary to estimate parameters in a complex multi-species model within a state-space modeling framework.

@@

knitr::kable(df_sp_list,
             format = "markdown",
             caption = "Fish species found in the study watersheds.")
```

@@

  cap[i] <- paste0("Theoretical predictions for the release effect in a ten-species community. Rows represent different response variables, and columns show distinct simulation scenarios with different strengths of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Other parameters are: ",
                       "number of species $S$ = ", df_param$n_species[i], "; intrinsic growth rate of an enhanced species $r_1$ = ", df_param$r1[i], "; maximum intrinsic growth rate of unenhanced species $r_{max}$ = ", df_param$r_max[i], "; environmental stochasticity $\\sigma_{\\varepsilon}$ = ", df_param$sd_env[i], "; carrying capacity $K$ = ", df_param$k[i], ".")

>>>>

**Species interaction.** We analyzed a subset of our data to estimate the strength of interspecific interactions among stream fishes. In this analysis, we focused on `r n_distinct(df_complete$site_id)` sites with $>16$ years of observations and no intentional release of masu salmon. Further, at each site, we confined our analysis to species that occurred more than four times. These additional constraints were necessary to estimate parameters in a complex multi-species model within a state-space modeling framework.

@@

knitr::kable(df_sp_list,
             format = "markdown",
             caption = "Fish species found in the study watersheds. Trait information is based on the literature [@gotoEcologicalMorphologicalDivergence1975;@gotoLifeHistoryDistibution1981;@ministryofenvironmentofjapanThreatenedWildlifeJapan2014;@natsumedaEvaluationEcologicalFeatures2010;@fishbaseFishBaseHttpsWww] and expert knowledge.")
```

@@

  cap[i] <- paste0("Theoretical predictions for the release effect in a ten-species community. Rows represent different response variables, and columns show distinct simulation scenarios with different strengths of interspecific competition ($\\bar{\\alpha}$) and relative fitness of captive-bred individuals ($f_R$). Lines are loess curves (mean) with shades indicating associated 95% confidence intervals. Other parameters are: ",
                       "number of species $S$ = ", df_param$n_species[i], "; intrinsic growth rate of an enhanced species $r_1$ = ", df_param$r1[i], "; maximum intrinsic growth rate of unenhanced species $r_{max}$ = ", df_param$r_max[i], "; environmental stochasticity $\\sigma_{\\varepsilon}$ = ", df_param$sd_env[i], "; carrying capacity $K$ = ", df_param$k[i], ".")
